Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-22 doc/paper.Rmd
duplicate label removed

```{r type2, fig.height = 5, fig.width = 5, out.width='0.7\\textwidth', fig.cap="Side-by-side comparison of type II error rates of methods CS1 and CS2 by size of optimization window $w_o$."}
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
errorsCV <- 
  rbind(errorrate(cvcs2, 0.001), 
        errorrate(cvcs2, 0.005), 
        errorrate(cvcs2, 0.01), 
        errorrate(cvcs2, 0.05))
errorsCV$method <- "CS2"

>>>>

```{r type22, fig.height = 5, fig.width = 5, out.width='0.7\\textwidth', fig.cap="Side-by-side comparison of type II error rates of methods CS1 and CS2 by size of optimization window $w_o$."}
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
errorsCV <- 
  rbind(errorrate(cvcs2, 0.001), 
        errorrate(cvcs2, 0.005), 
        errorrate(cvcs2, 0.01), 
        errorrate(cvcs2, 0.05))
errorsCV$method <- "CS2"
